MG7: Configurable and scalable 16S data analysis

### 2016-07-26 docs/mg7-paper/out/paper.tex
note about why this misassignment correction strategy, reusable for other data
start describing the mg7 database self-correction step

After this first step, we drop redundant assignments: if sequences
\(S_1 \subseteq S_2\) share an assignment \(T\), it gets dropped from
\(S_1\); sequences which as a result end up having no assignments are
removed.

Once we have non-redundant set of RNA sequences containing all those
corresponding to 16S, we can apply our procedure for checking internal
consistency of taxonomic assignments.

We run MG7 using this set of sequences as query, and with reference all
but the one we are trying to assign. Explain

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  which kind of misassignments can be detected
\item
  how
\item
  why it is OK for sequences assigned to strange taxa, with no close 16S
  seq (they will get no hits)
\item
  we analyze every assignment independently
\end{enumerate}

>>>>

After this first step, we drop redundant assignments: if sequences
\(S_1 \subseteq S_2\) share an assignment \(T\), it gets dropped from
\(S_1\); sequences which as a result of this process end up having no
assignments are removed.

Once we have non-redundant set of RNA sequences containing all those
corresponding to 16S, we can apply our procedure for checking internal
consistency of taxonomic assignments. We run MG7 using this set of
sequences as query, with reference all but the one we are trying to
assign. Under the (reasonable) assumption of 16S sequence similarity
being correlated with the taxonomy tree topology, the MG7 result should
either

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  be a taxon \emph{close} to the original assignment, if there are
  sequences similar enough in the reference database
\item
  be empty, due to this sequence having no similar sequences in the
  reference database
\end{enumerate}

In any other case, under our assumptions, this assignment should be
discarded.

All these steps are automated, and integrated with every release of our
reference database. The whole process can be repeated and adapted to
other subsets of RNACentral; we do this for a 18S reference database.
